Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2013-12-17 ms.tex
some clean-up, more needed

\begin{abstract}
We present full-sky maps of dust optical depth and temperature derived by 
applying the \cite{FDS99} two-component dust emission model fitted to 
\PLANCK~217, 353, 545, 857 GHz and \cite{SFD} \IRAS~100$\mu$m data. Both the 
optical depth and temperature maps have angular resolution of $6.1'$. Such maps
 serve as an important alternative to and comparison for other dust 
emission models, especially the single modified blackbody (MBB) model in which 
$\beta$ and $T$ both vary spatially. We also expect the derived optical 
depth to provide valuable cross-checks for other dust-column related data 
products, specifically the \cite{SFD} map, which assumed 
$\beta = 2$ single-component dust emission and included a temperature map of 
inferior $\sim$$1.3^{\circ}$ resolution. We briefly compare our 
best-fit two-component spectral energy distributions to those of the 
\cite{planckdust} single-component parametrization.
%mention the enhanced temperature resolution relative to SFD
%Our optical depth map will also provide a useful reference for dust maps 
%based on stellar colors rather than infrared emission.
\end{abstract}

\section{Introduction}
%why dust important in astronomy/astrophysics
The presence of Galactic interstellar dust affects
astronomical observations over a wide range of wavelengths. In the mid-infrared
and far-infrared, Galactic dust emission is a major contributor
to the observed sky intensity. At optical and ultraviolet wavelengths, 
extinction by foreground dust grains attenuates the signal from extragalactic 
sources over the entire sky. Understanding the properties of dust in the 
interstellar medium (ISM) is valuable in its own right, as the ISM is the site 
of star formation, thereby playing a crucial role in galaxy evolution. Equally,
 or perhaps even more important to the practice of astronomy, however, is 
accurately accounting for dust as a foreground which reddens optical/UV o
bservations and superimposes Galactic emission on low-frequency observations 
of the cosmic microwave background (CMB). 
%specify ``low frequency more precisely eventually
% somewhere mention re-radiation

@@

The \PLANCK~2013 data release \citep{planck2013} represents an important 
opportunity to revisit foreground predictions in light of \PLANCK's superb, 
relatively artifact-free broadband data covering the entire sky and a broad 
range of frequencies. \cite{planckdust} has recently conducted a study modeling
\PLANCK~353 GHz, 545 GHz, 857 GHz and IRAS 100$\mu$m emission with a single
MBB spectrum. Here we investigate the FDS99 two-component dust emission model 
as an alernative model for the dust SED composed of \PLANCK~and \IRAS~data. In
doing so, we obtain $6.1'$ resolution maps of dust temperature and optical 
depth. Because
we are using a model that has been validated using FIRAS data down to sub-mm
wavelengths, e expect our best-fit parameters to be useful in constructing high-resolution
 predictions of dust emission over a very broad range of wavelengths. This 
includes low frequencies ($<$350 GHz), which \cite{planckdust} caution their 
model may not adequately fit, and also data near the peak of the dust SED, for
 example \AKARI~140-160$\mu$m. We also anticipate our derived optical depth map
 will serve as a useful comparison for extinction estimates based 
directly upon optical/NIR observations of stars.

@@

In $\S$\ref{sec:data} we discuss the data used throughout this study. In 
$\S$\ref{sec:prepro} we describe our preprocessing of the data to isolate 
thermal emission from Galactic dust. In $\S$\ref{sec:modeling} we describe the 
dust emission model we fit to the \PLANCK and \IRAS~data. In 
$S$\ref{sec:fitting} we provide details of the Markov Chain Monte Carlo method 
with which we have estimated the parameters of our model. In 
$\S$\ref{sec:results} we present the full-sky maps of dust temperature and 
optical depth thus obtained, and conclude and $\S$\ref{sec:conclusion}

>>>>

\begin{abstract}
We present full-sky maps of dust optical depth and temperature derived by 
fitting the \cite{FDS99} two-component dust emission model to
\PLANCK~217, 353, 545, 857 GHz and \cite{SFD} \IRAS~100$\mu$m data. Both the 
optical depth and temperature maps have angular resolution of $6.1'$. Such maps
 serve as an important alternative to and comparison for other dust 
emission models, especially the single modified blackbody (MBB) model in which 
$\beta$ and $T$ both vary spatially. We also expect the derived optical 
depth to provide valuable cross-checks for other dust-column related data 
products, specifically the \cite{SFD} map, which assumed 
$\beta = 2$ single-component dust emission and included a temperature map of 
inferior $\sim$$1.3^{\circ}$ resolution. We briefly compare our 
best-fit two-component spectral energy distributions to those of the 
\cite{planckdust} single-component parametrization.
%mention the enhanced temperature resolution relative to SFD
%Our optical depth map will also provide a useful reference for dust maps 
%based on stellar colors rather than infrared emission.
\end{abstract}

\section{Introduction}
%why dust important in astronomy/astrophysics
The presence of Galactic interstellar dust affects
astronomical observations over a wide range of wavelengths. In the mid-infrared
and far-infrared, Galactic dust emission is a major contributor
to the observed sky intensity. At optical and ultraviolet (UV) wavelengths, 
extinction by foreground dust grains attenuates the signal from extragalactic 
sources over the entire sky. Understanding the properties of dust in the 
interstellar medium (ISM) is valuable in its own right, as the ISM is the site 
of star formation, thereby playing a crucial role in galaxy evolution. Equally,
 or perhaps even more important to the practice of astronomy, however, is 
accurately accounting for dust as a foreground which reddens optical/UV 
observations and superimposes Galactic emission on low-frequency observations 
of the cosmic microwave background (CMB). 
%specify ``low frequency more precisely eventually
% somewhere mention re-radiation

@@

The \PLANCK~2013 data release \citep{planck2013} represents an important 
opportunity to revisit foreground predictions in light of \PLANCK's superb, 
relatively artifact-free broadband data covering the entire sky and a wide 
range of frequencies. \cite{planckdust} has recently conducted a study modeling
\PLANCK~353 GHz, 545 GHz, 857 GHz and IRAS 100$\mu$m emission with a single
MBB spectrum. Here we investigate the FDS99 two-component dust emission model 
as an alernative model for the dust SED composed of \PLANCK~and \IRAS~data. In
doing so, we obtain $6.1'$ resolution maps of dust temperature and optical 
depth. Because
we are using a model that has been validated using FIRAS data down to sub-mm
wavelengths, we expect our best-fit parameters to be useful in constructing 
high-resolution
 predictions of dust emission over a very broad range of wavelengths. This 
includes low frequencies ($<$350 GHz), which \cite{planckdust} caution their 
model may not adequately fit, and also data near the peak of the dust SED, for
 example \AKARI~140-160$\mu$m. We also anticipate our derived optical depth map
 will serve as a useful comparison for extinction estimates based 
directly upon optical/NIR observations of stars.

@@

In $\S$\ref{sec:data} we discuss the data used throughout this study. In 
$\S$\ref{sec:prepro} we describe our preprocessing of the data to isolate 
thermal emission from Galactic dust. In $\S$\ref{sec:modeling} we describe the 
dust emission model we fit to the \PLANCK~and \IRAS~data. In 
$\S$\ref{sec:fitting} we provide details of the Markov Chain Monte Carlo method
with which we have estimated the parameters of our model. In 
$\S$\ref{sec:results} we present the full-sky maps of dust temperature and 
optical depth thus obtained, and conclude and $\S$\ref{sec:conclusion}
